\section{Results And Discussion}

	\subsection{Discussion Of Results}
	
	\subsection{Discussion Of Errors}
		Although some error was present in the measurement, the results were clear enough to draw concrete conclusions. Especially after the smoothing done by the software of the MCA, errors were less prominent.
	
		\subsubsection{Main Sources Of Errors}
			The main sources of error in this experiment are:
			\\
			\\
				\textbf{Angle Arrangement}: 
					The instrument used for angle arrangement was old and worn down which made it harder for us to see the exact values and align the setup. Also since the instrument was ruler-like, there are vision based errors as well as we used our eyes and hands for alignment. These factors played role in the error of the scattering angle value.
					\\
					\\
				\textbf{Shielding}: 
					Shielding is necessary for safety reasons, however, the excessive shielding of the surroundings and the radiation source itself caused an extra peak in the measured spectra. The radiation that scattered from the lead blocks that are used for shielding effected the result a lot, however since we are aware of this unwanted consequence, we are able to just ignore that peak during the analysis of the main experiment. It was also informative to see the clear consequence of shielding in the resulting spectra which allowed us to brainstorm on it. 
		\subsubsection{Error Mitigation}
			The errors caused by shielding is not very important here since it has little to no effect on the actual peaks that we want to analyze and safety of people in the laboratory is definitely more important than "cleaner data" since the radiation used in this experiment is very dangerous. 
			\\
			\\
			The errors caused by the angle arrangement can be mitigated by replacing the current instrument with a better one, or at least a new one. I suspect the error in the scattering angle doesn't affect our result very much.